---
title: "Assignment 3"
author: "Calvin Wong"
date: "9/15/2018"
output: html_document
---

```{r}
library(stringr)
```


3. Copy the introductory example. The vector name stores the extracted names.

```{r}
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
name
```

1) Use the tools of this chapter to rearrange the vector so that all elements conform to the standard first_name last_name.

```{r}
removeComma <- str_split(name, ", ", simplify = TRUE)
corrName <- str_c(removeComma[, 2], removeComma[, 1])
corrName <- str_replace(corrName, "([a-z])([A-Z])", "\\1 \\2")
corrName
```

2) Construct a logical vector indicating whether a character has a title . (i.e Rev. and Dr. )

```{r}
str_detect(corrName, "[[:alpha:]]{2,}\\.")
```

3) Construct a logical vector indicating whether a character has a middle name.

```{r}
str_detect(name, " [A-z]{1,}\\. ")
```

4. Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression.

1) [0-9]+\\$

A string that contains at least one number from 0 to 9 followed by the "$" symbol

```{r}
test = c("45678$", "1234", "8910$")
str_extract_all(test, "[0-9]+\\$")
```

2) \\b[a-z]{1,4}\\b

A string that contains an instance of a lowercase character up to 4 alphabets from a to z

```{r}
test1 = c("tennis", "net", "ball", "court", "girl")
str_extract_all(test1, "\\b[a-z]{1,4}\\b")
```

3) .*?\\.txt$

Any string followed by a .txt abbreviation
```{r}
test2 = c("bye.txt", "bye", "good.txt", "good")
str_extract_all(test2, ".*?\\.txt$")
```

4) \\d{2}/\\d{2}/\\d{4}

A string which is formatted 2 digits followed by /, twice, and ends with 4 digits. Similar to a date format.

```{r}
test3 = c("08/01/2000", "8/01", "08/01/00", "08/01/1999")
str_extract_all(test3, "\\d{2}/\\d{2}/\\d{4}")
```

5) <(.+?)>.+?</\\1>

A string between enclosed <> and </> characters

```{r}
test4 = c("<...>Hi</...>", "<...>Hi<...>", "Hi")
str_extract_all(test4, "<(.+?)>.+?</\\1>")
```

9. The following code hides a secret message. Crack it with R and regular expressions. 

Scanning the code reveals entries with capitalized letters. "Congratulations you are a supernerd"
```{r}
code = "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8pf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
paste(unlist(str_extract_all(code, "[[A-Z]]")), collapse = "")
```

