---
title: "Project 1"
author: "Calvin Wong"
date: "9/15/2018"
output: html_document
---

In this project, you’re given a text file with chess tournament results where the information has some structure. Your job is to create an R Markdown file that generates a .CSV file. 

Required: Player’s Name, Player’s State, Total Number of Points, Player’s Pre-Rating, and Average Pre Chess Rating of Opponents

Let's load the necessary packages to perform the assigned tasks.
```{r}
library(stringr)
library(DT)
library(data.table)

tournamentinfo <- readLines("https://raw.githubusercontent.com/cwong79/DATA607/Project-1/tournamentinfo.txt")
head(tournamentinfo)
```
From observation of the data table, we see that the text file is formatted in a way where the information is segmented into 2 lines. The first line contains player ID, name and points with win/loss information. The second line contains state and rating. I will first format the row data into 2 different sets, 1 set for each row. From there, I will extract the necessary information to a vector. Finally, I will combined these vectors to form a formatted database.

Let's begin by pulling all the data we need into a workable database.

```{r}
line1 <- seq(5, 196, 3) # start on applicable row to pull player and name
line2 <- seq(6, 196, 3) # start on applicable row to pull state and points
player <- as.integer(str_extract(tournamentinfo[line1], "\\d+")) # line 1, pull out player id
name <- str_replace_all(str_extract(tournamentinfo[line1],"([|]).+?\\1"),"[|]","") # line 1, pull out player name
points <- str_extract(tournamentinfo[line1], "\\d.\\d") # line 1, pull out points
state <- str_extract(tournamentinfo[line2], "[A-Z]{2}" ) # line 2, pull out state
rating <- as.integer(str_replace_all(str_extract(tournamentinfo[line2], "R: \\s?\\d{3,4}"), "R:\\s", "")) # line 2, player rating 
newtournamentinfo <- data.frame(player, name, state, points, rating) # combine vectors to form the required database
head(newtournamentinfo)
```

Now to calculate average opponent rating. I have the opponent information available from line 1, I will need to extract opponents rankings based on player number and store the values into an opponent variable. I then created a loop to calculate average rankings and insert the value into a vector named avgopponent.

```{r}
opponents <- str_extract_all(str_extract_all(tournamentinfo[line1], "\\d+\\|"), "\\d+")

avgopponent <- length(line1)
for (i in 1:length(line1)) 
{ 
  avgopponent[i] <- round(mean(rating[as.numeric(unlist(opponents[player[i]]))]), digits = 0)
}
avgopponent
```
Finally, lets add the avgopponent variable to our completed database. I named this database newtournamentinfo1.

```{r}
newtournamentinfo1 <- data.frame(player, name, state, points, rating, avgopponent)
head(newtournamentinfo1)
```

With the completed table, I wrote to a csv file and called it newtournamentinfo as per assignment instructions.

```{r}
write.csv(newtournamentinfo1, file = "newtournamentinfo.csv")
```

