---
title: "Week 7 - Assignment"
author: "Calvin Wong"
date: "10/13/2018"
output: html_document
##toc: true
##toc_float: true
##theme: flatly
##highlight: monochrome
---

Pick three of your favorite books on one of your favorite subjects. At least one of the books should have more than one author. For each book, include the title, authors, and two or three other attributes that you find interesting.
Take the information that you’ve selected about these three books, and separately create three files which store the book’s information in HTML (using an html table), XML, and JSON formats (e.g. “books.html”, “books.xml”, and “books.json”). To help you better understand the different file structures, I’d prefer that you create each of these files “by hand” unless you’re already very comfortable with the file formats.

Here are the three books I chose for this assignment.

| id | title                   | author            | year | genre      | rating |
|----|-------------------------|-------------------|------|------------|--------|
| 1  | A Brief History of Time | Stephen Hawking   | 2011 | Science    | 4.5    |
| 2  | Kitchen Confidential    | Anthony Bourdain  | 2008 | Gastronomy | 4.6    |
| 3  | The Silent Oligarch     | Christopher Jones | 2012 | Fiction    | 3.5    |

***

```{r setup, include = F}
knitr::opts_chunk$set(echo = TRUE)

library(XML)
library(RCurl)
library(stringr)
library(knitr)
library(kableExtra)
library(jsonlite)

options(knitr.table.format = "html")
```

Here is the HTML loading method I used,

```{r}

html <- getURL("https://raw.githubusercontent.com/cwong79/DATA607/master/books.html")
html_raw <- readHTMLTable(html, header=TRUE, which=1, stringsAsFactors=FALSE)
html_books <- data.frame(html_raw)
html_books %>% kable() %>% kable_styling()
str(html_books)
```

***

Here is the XML loading method I used,

```{r}
xml <- getURL("https://raw.githubusercontent.com/cwong79/DATA607/master/books.xml")
xml_raw <- xmlParse(xml)
xml_books <- xmlToDataFrame(xml_raw, stringsAsFactors = FALSE)
xml_books %>% kable() %>% kable_styling()
str(xml_books)
```

***

Here is the JSON loading method I used,

```{r}
json <- getURL("https://raw.githubusercontent.com/cwong79/DATA607/master/books.json")
json_raw <- fromJSON(json)
json_books <- data.frame(json_raw, stringsAsFactors = FALSE)
json_books %>% kable() %>% kable_styling()
str(json_books)
```

Write R code, using your packages of choice, to load the information from each of the three sources into separate R data frames. Are the three data frames identical?

There are slight variances in the headers. I believe this occured due to the formatting of each data frame. The variables are all alike with identical values.
