---
title: "Week 5 - Assignment"
author: "Calvin Wong"
date: "9/29/2018"
output: html_document
---

The chart above describes arrival delays for two airlines across five destinations. Your task is to:
(1) Create a .CSV file (or optionally, a MySQL database!) that includes all of the information above. You’re encouraged to use a “wide” structure similar to how the information appears above, so that you can practice tidying and transformations as described below.

https://raw.githubusercontent.com/cwong79/DATA607/master/flights.csv

(2) Read the information from your .CSV file into R, and use tidyr and dplyr as needed to tidy and transform your data.

I used mysql to create the appropriate csv file with untidy information. My goal was to to tidy the data and have it into two structures so I can begin my analysis.
```{r}
library(tidyverse)
library(knitr)
library(gridExtra)

url <- "https://raw.githubusercontent.com/cwong79/DATA607/master/flights.csv"
flight <- read_csv(url)

## remove NULL row based on rule
newflight <- select(flight, -1) %>% filter(Schedule != "NULL" )

## loop replacement for NULL values. If NULL value is found, the loop will assign a value from the entry above.
for(i in 2:nrow(newflight)) {
  if(newflight$Airlines[i] == "NULL"){
    newflight$Airlines[i] <- newflight$Airlines[i-1]
  }
}

## convert char values into workable integers
newflight[, c(3:7)] <- sapply(newflight[, c(3:7)], as.integer)

## apply tidyverse functions
tidyflight <- newflight %>% gather(City, Count, 3:7) %>% spread(Schedule, Count) %>% mutate(`total flight`=delayed+`on time`)
tidyflight

## created another dataset to show delayed ratios
flightbyairlines <- tidyflight %>% group_by(Airlines) %>% summarise(delayed=sum(delayed), `on time`=sum(`on time`), `total flight`=delayed+`on time`, `delayed ratio`=delayed/`total flight`) 
flightbyairlines
```

(3) Perform analysis to compare the arrival delays for the two airlines.

Lets look at total flights graphically to get an idea how flights from cities are distributed
```{r}
ggplot(tidyflight) + geom_bar(aes(x=Airlines, y=`total flight`, fill=Airlines), stat = "identity") + facet_wrap(~ City, nrow = 1) + theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
```

Based on the cumulative flight data for both airlines, we can see Alaska flying approximately less than half of Amwest but has a higher amount of delayed flights.
```{r}
p1 <- ggplot(flightbyairlines) + geom_bar(aes(x=Airlines, y=`total flight`, fill=Airlines), stat = "identity")
p2 <- ggplot(flightbyairlines) + geom_bar(aes(x=Airlines, y=`delayed ratio`, fill=Airlines), stat = "identity")
grid.arrange(p1, p2, nrow=1)
```

We can conclude that Amwest is more effective at managing delayed flights.

(4) Your code should be in an R Markdown file, posted to rpubs.com, and should include narrative descriptions of your data cleanup work, analysis, and conclusions. Please include in your homework submission:
 The URL to the .Rmd file in your GitHub repository. and
 The URL for your rpubs.com web page.
